Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Abstracting abstract machines (AAM) is a systematic methodology 
  for constructing abstract interpreters that derived from concrete
  small-step abstract machines. Recent progress applies the same idea 
  on definitional interpreter and obtains a big-step 
  abstracting definitional interpreter (ADI) written in monadic style.
  Danvy shows the correspondence between abstract machines and interpreters.
  In this paper, we study the relations between small-step AAM and 
  big-step ADI.

  We show their correspondence and how to syntactically transform a small-step 
  abstracting abstract machine to a big-step abstracting definitional 
  interpreter.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification(un-CPS), and all of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediary form of 
  abstract interpreter.
  Remarkably, follow the idea that evaluation contexts are defunctionalized 
  continuations, we reveal how precise call/return match in control-flow 
  analysis is obtained by refunctionalizing a small-step abstracting 
  abstract machine,  % with unbounded stack
  as well as explain how it been lost by defunctionalizing the higher-order
  continuations into an algebraic data type. Further, we show how to turn 
  precise call/return match into computable analysis.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Abstracting abstract machines (AAM) is a systematic methodology 
  for constructing abstract interpreters that derived from concrete
  small-step abstract machines. Recent progress applies the same idea 
  on definitional interpreter and obtains a big-step 
  abstracting definitional interpreter (ADI) written in monadic style.
  Danvy shows the correspondence between concrete abstract machines and interpreters.
  But the relations between small-step abstracting abstract machines and 
  big-step abstracting definitional interpreters is not well studied.

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstracting abstract machines into big-step abstracting definitional 
  interpreters.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style). All of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediary form of 
  abstract interpreter.
  Remarkably, follow the idea that evaluation contexts are defunctionalized 
  continuations, we reveal how precise call/return match in control-flow 
  analysis can be obtained by refunctionalizing a small-step abstracting 
  abstract machine,
  as well as explain how it been lost by defunctionalizing the higher-order
  continuations into an firts-order data type.
